%-------------------------
% Resume in Latex
% Author : Alexandru Ilies
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6.5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alexandru Ilies} \\ \vspace{0.7pt}
    \href{mailto:alex.ilies@icloud.com}{\underline{alex.ilies@icloud.com}} $|$
    \href{https://alexilies.page.link/in}{\underline{linkedin.com/in/alex-ilies}} $|$
    \href{https://github.com/hackmajoris}{\underline{github.com/hackmajoris}}
\end{center}

%-----------PROFESSIONAL-SUMMARY-----------
\section{Professional Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{{Senior Software Engineer and AWS-certified Cloud Architect with 11 years of experience designing and delivering production systems at scale. Specialized in event-driven serverless architectures on AWS, leading teams of up to 10 across 5+ projects, owning the full infrastructure lifecycle for platforms serving 35,000+ users, and working as a forward deployment engineer close to customers and real-world delivery. Holds 4 AWS certifications including Security Specialty and DevOps Professional.}}}
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: TypeScript, JavaScript, Go, Java, Python, Swift} \\
     \textbf{Frameworks \& Runtime}{: Angular, React, NestJS, Node.js, Spring, Tailwind, iOS/WatchOS} \\
     \textbf{Cloud \& Infrastructure}{: AWS (ECS, Lambda, SQS, SNS, EventBridge, CloudWatch, RDS, DynamoDB), Terraform, CDK, CloudFormation, Docker} \\
     \textbf{Databases}{: PostgreSQL, DynamoDB (Single/Multi-Table Design), MongoDB, Aurora, Redis} \\
     \textbf{DevOps \& Tooling}{: GitHub Actions, GitLab CI/CD, Docker, Nx, Git} \\
     \textbf{Architecture \& Leadership}{: Event-Driven Architecture, Serverless, Microservices, Technical Mentoring, System Design}
     }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Lead Software Engineer}{Jan. 2020 -- Present}
      {msg.group}{Cluj, RO}
      \resumeItemListStart
        \resumeItem{Architected and owned the complete cloud infrastructure for a crowd testing platform serving 35,000+ users, using 20+ AWS services including ECS, Lambda (30+), SQS, SNS, EventBridge, and CloudWatch.}
        \resumeItem{Led a team of up to 10 developers across frontend and backend, driving code quality through structured reviews, automated testing, and mentorship programs.}
        \resumeItem{Implemented event-driven, serverless architectures that improved system scalability and reduced operational costs through continuous optimization.}
        \resumeItem{Established CI/CD pipelines with GitHub Actions and GitLab CI, enabling multiple deployments per day with zero-downtime releases.}
        \resumeItem{Defined and enforced security best practices across all projects --- WAF, IAM policies, secrets management --- aligned with AWS Security Specialty certification.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July. 2015 -- Dec. 2019}
      {msg.group}{Cluj, RO}
      \resumeItemListStart
        \resumeItem{Progressed from junior to mid-level engineer across multiple client projects, building full-stack web applications with Angular, TypeScript, and Node.js.}
        \resumeItem{Delivered full feature modules --- ticketing, user rewards, and public-facing portals --- for a German public sector platform serving citizens nationwide.}
        \resumeItem{Built first cloud-native solutions on AWS, gaining hands-on expertise that led to 4 AWS certifications.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Passbrains} $|$ Lead Developer \& Cloud Architect $|$ \emph{AWS (ECS, Lambda, SQS, SNS, EventBridge, CDK), Angular, NestJS}}{}
          \resumeItemListStart
            \resumeItem{Led the complete re-architecture of a public crowd testing platform serving 35,000+ users, from monolith to event-driven serverless.}
            \resumeItem{Designed and deployed 30+ Lambda functions orchestrated via EventBridge and SQS/SNS for asynchronous processing.}
            \resumeItem{Managed infrastructure as code with CDK and Terraform, enabling reproducible multi-environment deployments.}
            \resumeItem{Drove DevSecOps adoption --- automated vulnerability scanning, secrets rotation, and compliance checks in CI/CD pipelines.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Dipko} $|$ Full-Stack Developer $|$ \emph{AWS, Angular, TypeScript, Node.js}}{}
          \resumeItemListStart
            \resumeItem{Built a German public sector platform aggregating government institutions into a unified citizen-facing portal.}
            \resumeItem{Deployed cloud-based solutions on AWS tailored to public sector compliance and availability requirements.}
          \resumeItemListEnd

     \resumeProjectHeading
          {\textbf{Personal Tools} $|$ \emph{AWS, React, TypeScript, Go, Java}}{}
          \resumeItemListStart
            \resumeItem{Serverless reverse proxy and link shortener: \href{https://l.dot-core.com}{\underline{l.dot-core.com}}}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION & CERTIFICATIONS-----------
\section{Education \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical University of Cluj-Napoca}{Cluj, RO}
      {Bachelor in Computer Science}{Oct. 2012 -- July 2016}
  \resumeSubHeadingListEnd
  \vspace{-6pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \begin{tabular*}{0.97\textwidth}{l@{\hspace{0.15\textwidth}}l}
      \textbf{AWS Security Specialty} \href{https://links.dot-core.com/a338e1}{\underline{Verify}} & \textbf{AWS DevOps Professional} \href{https://links.dot-core.com/1f077f}{\underline{Verify}} \\
      \textbf{AWS Associate Developer} \href{https://links.dot-core.com/f74686}{\underline{Verify}} & \textbf{AWS Associate Architect} \href{https://links.dot-core.com/e6f1c2}{\underline{Verify}} \\
    \end{tabular*}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
